\section{Sub-surveys} \label{app:subsurveys}

In the following tables, each cell should be understood as a sentence token that belongs to a particular token set and type based on its row and column indices. For example, the cell whose row name is ``TS-6" and whose column name ``UCAT-LF'' is a sentence token from the token set 6 and represents the type: unlike category like function coordination. A symbol inserted in this cell, which is $\alpha$ in this case, signifies that this sentence is assigned to the survey symbolised as $\alpha$, which is Survey 1. 

\subsection{Category block}

\begin{tabular}{|c|c|c|c|c|}
	\hline
	 & \textbf{LCAT-LF} & \textbf{UCAT-LF} & \textbf{LCAT-UF} & \textbf{UCAT-UF} \\ \hline
	TS-1 & $\alpha$ & $\beta$ & $\gamma$ & $\delta$ \\ \hline
	TS-2 & $\delta$ & $\alpha$ & $\beta$ & $\gamma$ \\ \hline
	TS-3 & $\gamma$ & $\delta$ & $\alpha$ & $\beta$ \\ \hline
	TS-4 & $\beta$ & $\gamma$ & $\delta$ & $\alpha$ \\ \hline
	TS-5 & $\alpha$ & $\beta$ & $\gamma$ & $\delta$ \\ \hline
	TS-6 & $\delta$ & $\alpha$ & $\beta$ & $\gamma$ \\ \hline
	TS-7 & $\gamma$ & $\delta$ & $\alpha$ & $\beta$ \\ \hline
	TS-8 & $\beta$ & $\gamma$ & $\delta$ & $\alpha$ \\ \hline
	TS-9 & $\alpha$ & $\beta$ & $\gamma$ & $\delta$ \\ \hline
	TS-10 & $\delta$ & $\alpha$ & $\beta$ & $\gamma$ \\ \hline
	TS-11 & $\gamma$ & $\delta$ & $\alpha$ & $\beta$ \\ \hline
	TS-12 & $\beta$ & $\gamma$ & $\delta$ & $\alpha$ \\ \hline
\end{tabular}
\quad
\begin{tabular}{|c|c|}
	\hline
	\textbf{Symbol} & \textbf{Survey} \\ \hline
	$\alpha$ & Survey 1 \\ \hline
	$\beta$ & Survey 2 \\ \hline
	$\gamma$ & Survey 3 \\ \hline
	$\delta$ & Survey 4 \\ \hline
\end{tabular}



\subsection{Case block}

\begin{tabular}{|c|c|c|c|}
	\hline
	 & \textbf{LCASE-LF} & \textbf{UCASE-LF} & \textbf{UCASE-UF} \\ \hline
	TS-1 & $\alpha$ & $\delta$ & $\gamma$ \\ \hline
	TS-2 & $\beta$ & $\alpha$ & $\delta$ \\ \hline
	TS-3 & $\gamma$ & $\beta$ & $\alpha$ \\ \hline
	TS-4 & $\delta$ & $\gamma$ & $\beta$ \\ \hline
	TS-5 & $\alpha$ & $\delta$ & $\gamma$ \\ \hline
	TS-6 & $\beta$ & $\alpha$ & $\delta$ \\ \hline
	TS-7 & $\gamma$ & $\beta$ & $\alpha$ \\ \hline
	TS-8 & $\delta$ & $\gamma$ & $\beta$ \\ \hline
	TS-9 & $\alpha$ & $\delta$ & $\gamma$ \\ \hline
	TS-10 & $\beta$ & $\alpha$ & $\delta$ \\ \hline
	TS-11 & $\gamma$ & $\beta$ & $\alpha$ \\ \hline
	TS-12 & $\delta$ & $\gamma$ & $\beta$ \\ \hline
\end{tabular}
\quad
\begin{tabular}{|c|c|}
	\hline
	\textbf{Symbol} & \textbf{Survey} \\ \hline
	$\alpha$ & Survey 1 \\ \hline
	$\beta$ & Survey 2 \\ \hline
	$\gamma$ & Survey 3 \\ \hline
	$\delta$ & Survey 4 \\ \hline
\end{tabular}

\section{Instructions} \label{app:instruct}
\subsection{Turkish original}

\begin{center}
	\large \textbf{Sayfa 1/2}
\end{center}


\textbf{Lütfen ankete başlamadan önce yönergeleri dikkatle okuyunuz ve anladığınıza emin olunuz.}

Bu ankette size ardı ardına farklı Türkçe cümleler gösterilecek. Öncelikle gösterilen cümleyi dikkatle okuyunuz. Ardından bu cümleyi günlük hayatınızda duyduğunuz veya okuduğunuz bir durum hayal etmeye çalışın.

Örnek durumlardan bazıları: 

\begin{itemize}
	\item Sokaktaki birinin bu cümleyi kurmuş olması
	\item Afiş, mesaj, kitapçık, sosyal medya postu veya reklam panolarında okumuş olmanız.
\end{itemize}


\begin{sloppypar}
	
	Kendinizi bu duruma koyduktan sonra, bu cümleye olan dilsel tepkinizi \mbox{(--3) ve (3)} ölçeği üzerinden puanlandırınız. Ölçeğin uç noktaları şöyle yorumlanmalıdır: 
	
\end{sloppypar}

(3): Anadili Türkçe olan biri tarafından kurulmuş gibi duyulan bir cümle. Tamamen doğal ve anlaşılabilir. 



(--3): Anlaşılması oldukça güç (hatta anlam ifade etmeyen), garip duyulan ve Türkçeyi yeni öğrenen bir yabancı tarafından kurulmuş olması oldukça muhtemel.


Eğer gösterilen cümleye olan tepkiniz bu iki uç nokta arasında ise aradaki değerleri tepkinizin derecesine göre kullanınız. Örneğin, oldukça doğal duyulan fakat az da olsa bir gariplik barındıran cümle için (1) veya (2) kullanılabilir. 

\vspace{10pt}
\textbf{
	Anket sırasında verdiğiniz puanlar cümleden cümleye önemli değişiklikler gösterebilir.}

\newpage
\begin{center}
	\large \textbf{Sayfa 2/2}
\end{center}

\textbf{ÖNEMLİ NOKTALAR:}

\begin{itemize}
	\item Bu ankette DOĞRU veya YANLIŞ cevap kavramı bulunmamaktadır. Cümleleri puanlarken okulda öğrenmiş olduğunuz çeşitli dilbilgisi ve yazım kurallarını göz önünde bulundurmayınız. Bu çalışma için önemli olan sizin anadili Türkçe olan biri olarak Türkçenin günlük hayattaki kullanımına dair içgüdüsel yaklaşımınızı tespit etmektir.
	\item Bazı cümlelerin ifade ettiği fikirlere kişisel olarak katılmıyor olabilirsiniz. Fakat bu çalışma için önemli olan cümlelerin ifade ettiklerine karşı olan tutumunuz \textbf{DEĞİL}, cümleleri ne kadar anlaşılabilir ve doğal bulduğunuzdur.
\end{itemize}

\textbf{Bazı örnek cümlelerin değerlendirilmesi:}


Gösterilen bazı cümlelerdeki yazım biçimleri anadili Türkçe olan kişilerin günlük hayattaki konuşmalarını yansıtacak şekilde olabilir. Eğer aşağıdaki cümle size anadili Türkçe olan biri tarafından kurulmuş gibi duyuluyorsa, yazım biçimini görmezden geliniz.

\begin{enumerate}
	\item ``Dersten sonra ananemlere uğrıycam.''
\end{enumerate}


Aşağıdaki örnek cümleyi değerlendirirken bu cümlenin fikir düzeyinde ne ifade ettiğini dikkate almayınız. Eğer gösterilen cümle anlamını sorunsuz bir şekilde iletebiliyorsa, bu cümle kişisel görüşlerinizden bağımsız olarak yüksek bir puan almalıdır.


\begin{enumerate}
	\setcounter{enumi}{1}
	\item ``Monarşilerin yıkılmasıyla beraber acınası ve zavallı bir dünyada yaşar olduk.''
\end{enumerate}



\subsection{English translation}

\begin{center}
	\large \textbf{Page 1/2}
\end{center}

\textbf{Please carefully read and make sure that you fully understand the instructions before starting the survey.}

In this survey, you will be shown distinct sentences in Turkish one after the other. First of all, carefully read the sentence shown. Then try to imagine a situation where you hear or read this sentence in your daily life. Some example situations:

\begin{itemize}
	\item Some stranger on the street utters this sentence
	\item You read it on a poster, message, booklet, social media post or billboard.
\end{itemize}

After you put yourself in a situation, rate your linguistic response to this sentence on a scale from ($-$3) to (3). The endpoints of the scale should be interpreted as follows:

(3): A sentence that sounds like it is constructed by a native Turkish speaker. It is completely natural and fully understandable. 

($-$3): It is quite likely that the sentence is uttered by a foreigner who just started learning Turkish and it is very difficult to understand (might even be outright incomprehensible) and sounds quite strange.

If your reaction to the sentence shown is somewhere between these two extremes, use the values in-between according to the degree of your reaction. For instance, (1) or (2) can be
used for a sentence that sounds quite natural with a little bit of awkwardness. Feel free to use the intermediate values between the endpoints accordingly.

\textbf{The scores you employ during the survey can vary significantly from sentence to sentence.}

\begin{center}
	\large \textbf{Page 2/2}
\end{center}

\textbf{Important points to consider:}
\begin{itemize}
	\item There is no concept of TRUE or FALSE answers in this questionnaire. When scoring sentences, do not take into account the various grammar and spelling rules you learned in your education. For the survey, what is important is your instinctive approach to the use of Turkish in daily life as a native speaker of Turkish.
	
	\item You may not personally agree with the ideas expressed by some sentences. However, what is important for this survey is \textbf{NOT} your attitude towards what the
	sentences express, but how understandable and natural you find the sentences. 
\end{itemize}


\textbf{Evaluation of some sample sentences:}\\
The spellings in some of the sentences shown may reflect the daily speech of native Turkish speakers. If the following sentence sounds like it is constructed by a native Turkish speaker, the unorthodox spelling must be ignored when scoring.

\begin{enumerate}
	
	\item ``I'll stop by my grandma after class.''\footnote{Here the original Turkish sentence was: ``Dersten sonra ananemlere uğrıycam.'' which utilises a type of spelling that better reflects the phonetic aspects of daily speech. However, this kind of spelling is frowned upon both in formal and semi-formal written contexts. Especially the ``educated'' stratum of the Turkish society tend to be extremely sensitive to various orthography (often confused with grammar) rules.}
\end{enumerate}


When evaluating the example sentence below, do not take into account what this sentence expresses at the idea level. If the sentence shown can convey its meaning without any problems and sounds natural, this sentence should receive a high rating regardless of your personal opinions/worldview.

\begin{enumerate}
	\setcounter{enumi}{1}
	\item ``With the collapse of monarchies, we found ourselves living in a pathetic and poor world.''
\end{enumerate}


\section{Glossed materials}
\subsection{Coordination of unlike categories}

\pex[exno=TS1, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS1} 
\a
\begingl
\gla {[} Zengin bir {memur }]NP\textsubscript{\textsc{pred}} veya {[} çok saygın {biri }]NP\textsubscript{\textsc{pred}} ol-abil-ir.//
\glb rich \textsc{indf.det} officer or very respected person be-\textsc{abil}-\textsc{aor} //
\glft `He/she can be a rich officer or a very respected person.' //
\endgl
\a
\begingl
\gla {[} Zengin bir {memur }]NP\textsubscript{\textsc{pred}} veya {[} çok + {saygın }]AdjP\textsubscript{\textsc{pred}} ol-abil-ir.  //
\glb rich \textsc{indf.det} officer or very respected be-\textsc{abil}-\textsc{aor} //
\glft `He/she can be a rich officer or very respected.' //
\endgl
\a
\begingl
\gla {[} Saygın bir {memur-u }]NP\textsubscript{\textsc{obj}} ve {[} kendi {ofis-i-nde }]NP\textsubscript{\textsc{adjunct}} tebrik et-ti-m.  //
\glb respected \textsc{indf.det} officer-\textsc{acc} and own office-\textsc{3P}-\textsc{loc} congratulation do-\textsc{pst}-\textsc{1sg} //
\glft `I congratulated a respected officer and in his/her own office.' //
\endgl
\a
\begingl
\gla {[} Saygın bir { memur-u }]NP\textsubscript{\textsc{obj}} ve + {[} {inanarak }]AdvP\textsubscript{\textsc{adjunct}} tebrik et-ti-m.  //
\glb respected \textsc{indf.det} officer-\textsc{acc} and believe-\textsc{advz} congratulation do-\textsc{pst}-\textsc{1sg} //
\glft `I congratulated a respected officer and faithfully.' //
\endgl
\xe 



\pex[exno=TS2,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS2}
\a
\begingl
\gla {[[} Araba-lar ve {arkadaşlık }] { hakkında }]PP\textsubscript{\textsc{obj}} konuş-tu-k. //
\glb {} car-\textsc{pl} and friendship about talk-\textsc{pst}-\textsc{1pl} //
\glft `We talked about cars and friendship.' //
\endgl
\a
\begingl
\gla Arkadaşlığ-ımız hakkında {[} saygı + {çerçeve-si-nde }]NP\textsubscript{\textsc{adjunct}} ve {[} {uzun-ca }]AdvP\textsubscript{\textsc{adjunct}} konuş-tu-k.//
\glb friendship-\textsc{1pl.poss} about respect framework-\textsc{3p}-\textsc{loc} and long-\textsc{advz}  talk-\textsc{pst}-\textsc{1pl} //
\glft `We talked respectfully and at length about our friendship.' //
\endgl
\a 
\begingl
\gla {[} İki arkadaş { gibi }]PP\textsubscript{\textsc{adjunct}} ve {[} araba-lar  + { hakkında }]PP\textsubscript{\textsc{obj}} konuş-tu-k. //
\glb two friend like and car-\textsc{pl} about talk-\textsc{pst}-\textsc{1pl} //
\glft `We talked about cars and like two friends.' //
\endgl
\a
\begingl
\gla {[} {Uzun-ca }]AdvP\textsubscript{\textsc{adjunct}} ve {[} { arkadaşlığ-ımız-ı }]NP\textsubscript{\textsc{obj}} konuş-tu-k. //
\glb long-\textsc{advz} and friendship-\textsc{1pl.poss}-\textsc{acc}  talk-\textsc{pst}-\textsc{1pl} //
\glft `We talked at length and our friendship.' //
\endgl
\xe

\pex[exno=TS3,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS3} 
\a
\begingl
\gla Bu-ndan sonra her şey-i {[[} kendi kariyer-im ve {çıkar-lar-ım }] { için }]PP\textsubscript{\textsc{adjunct}} düşün-eceğ-im. //
\glb this-\textsc{abl} after every thing-\textsc{acc} {} own career-\textsc{1sg.poss} and interest-\textsc{pl}-\textsc{1sg.poss} for think-\textsc{fut}-\textsc{1sg} //
\glft `From now on, I will think of everything for my own career and interests.' //
\endgl
\a \begingl
\gla Bu-ndan sonra her şey-i {[} kendi kariyer-im-e { göre }]PP\textsubscript{\textsc{adjunct}} ve {[} {bencil-ce }]AdvP\textsubscript{\textsc{adjunct}} düşün-eceğ-im. //
\glb this-\textsc{abl} after every thing-\textsc{acc} own career-\textsc{1sg.poss}-\textsc{dat} {according to} and selfish-\textsc{advz} think-\textsc{fut}-\textsc{1sg} //
\glft `From now on, I will think of everything according to my own career and selfishly.' //
\endgl
\a
\begingl
\gla Bu-ndan sonra {[} her { gün }]NP\textsubscript{\textsc{adjunct}} ve {[} kendi {kariyer-im-i }]NP\textsubscript{\textsc{obj}} düşün-eceğ-im. //
\glb this-\textsc{abl} after every day and own career-\textsc{1sg.poss}-\textsc{acc} think-\textsc{fut}-\textsc{1sg} //
\glft `From now on, I will think every day and about my career.' //
\endgl
\a
\begingl
\gla Bu-ndan sonra {[} kendi { kariyer-im-i }]NP\textsubscript{\textsc{obj}} ve {[} { sakin-ce }]AdvP\textsubscript{\textsc{adjunct}} düşün-eceğ-im. //
\glb this-\textsc{abl} after own career-\textsc{1sg.poss}-\textsc{acc} and calm-\textsc{advz} think-\textsc{fut}-\textsc{1sg} //
\glft `From now on, I will think about my own career and calmly.' //
\endgl
\xe


\pex[exno=TS4,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS4}
\a 
\begingl
\gla  Bu {[} {savaş-lar }]NP\textsubscript{\textsc{subj}} ve {[} {isyan-lar }]NP\textsubscript{\textsc{subj}} + toprak-lar-ımız-da yıl-lar-ca sür-dü. //
\glb this war-\textsc{pl} and rebellion-\textsc{pl} land-\textsc{pl}-\textsc{1pl.poss}-\textsc{loc} year-\textsc{pl}-\textsc{advz} continue-\textsc{pst} //
\glft `These wars and rebellions continued for years in our lands.' //
\endgl
\a
\begingl
\gla Bu isyan-lar {[} yıl-lar { boyunca }]PP\textsubscript{\textsc{obl}} ve {[} her { gün }]NP\textsubscript{\textsc{obl}} sür-dü. //
\glb this rebellion-\textsc{pl} year-\textsc{pl} throughout and every day continue-\textsc{pst} // 
\glft `These rebellions lasted for years and every day.' //
\endgl
\a
\begingl
\gla {[} Bu  {savaş-lar }]NP\textsubscript{\textsc{subj}} ve {[} {toprak-lar-ımız-da }]NP\textsubscript{\textsc{adjunct}} yıl-lar-ca sür-dü. //
\glb this war-\textsc{pl} and land-\textsc{pl}-\textsc{1pl.poss}-\textsc{loc} year-\textsc{pl}-\textsc{advz} continue-\textsc{pst} //
\glft `These wars and in our lands lasted for years.' //
\endgl
\a
\begingl
\gla {[} Bu  {savaş-lar }]NP\textsubscript{\textsc{subj}} ve {[} {yıl-lar-ca}]AdvP\textsubscript{\textsc{adjunct}} sür-dü.//
\glb this war-\textsc{pl} and year-\textsc{pl}-\textsc{advz} continue-\textsc{pst} //
\glft `These wars and for years lasted.' //
\endgl
\xe



\pex[exno=TS5,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS5} 
\a
\begingl
\gla Baba-m {[} {abi-m-e }]NP\textsubscript{\textsc{obl}} ve {[} {bana }]NP\textsubscript{\textsc{obl}} aylık harçlık-lar-ımız-ı banka transfer-i-(y)le yolla-dı. //
\glb father-\textsc{1sg.poss} brother-\textsc{1sg.poss}-\textsc{dat} and me.\textsc{dat} monthly allowance-\textsc{pl}-\textsc{1pl.poss}-\textsc{acc} bank transfer-\textsc{3p}-\textsc{ins} send-\textsc{pst} //
\glft `My father sent our monthly allowances to my brother and me by bank transfer.' //
\endgl
\a
\begingl
\gla Baba-m abi-m-e aylık harçlığ-ı-nı {[} banka {transfer-i-(y)le }]NP\textsubscript{\textsc{adjunct}} ve {[} {aksatmadan }]AdvP\textsubscript{\textsc{adjunct}} yolla-(y)abil-miş.//
\glb father-\textsc{1sg.poss} brother-\textsc{1sg.poss}-\textsc{dat} monthly allowance-\textsc{3p}-\textsc{acc} bank transfer-\textsc{3p}-\textsc{ins} and {without delay} send-\textsc{abil}-\textsc{pst} //
\glft `My father was able to send his monthly allowance to my brother by bank transfer and without delay.' //
\endgl
\a
\begingl
\gla Baba-m {[} {abi-m-e }]NP\textsubscript{\textsc{obl}} ve {[} aylık {harçlığ-ı-nı }]NP\textsubscript{\textsc{obj}} banka transfer-i-(y)le yolla-(y)abil-miş.//
\glb father-\textsc{1sg.poss} brother-\textsc{1sg.poss}-\textsc{dat} and monthly allowance-\textsc{3p}-\textsc{acc} bank transfer-\textsc{3p}-\textsc{ins} send-\textsc{abil}-\textsc{pst.3sg} //
\glft `My father was able to send my brother and his monthly allowance by bank transfer.' //
\endgl
\a
\begingl
\gla Baba-m aylık harçlığ-ı-nı {[} {abi-m-e }]NP\textsubscript{\textsc{obl}} ve {[} {aksatmadan }]AdvP\textsubscript{\textsc{adjunct}} yolla-mış.//
\glb father-\textsc{1sg.poss} monthly allowance-\textsc{3p}-\textsc{acc} brother-\textsc{1sg.poss}-\textsc{dat} and {without delay} send-\textsc{pst} //
\glft `My father sent his monthly allowance to my brother and without delay.' //
\endgl
\xe


\pex[exno=TS6,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS6} 
\a
\begingl
\gla Kardeş-im-in iş-ler-i-ni {[} {hızlı-ca }]AdvP\textsubscript{\textsc{adjunct}} ve {[} {yorulmadan }]AdvP\textsubscript{\textsc{adjunct}} hallet-ti-k. //
\glb brother-\textsc{1sg.poss}-\textsc{gen} business-\textsc{pl}-\textsc{3p}-\textsc{acc} quick-\textsc{advz} and {without getting tired} {take care}-\textsc{pst}-\textsc{1pl}  //
\glft `We took care of my brother's affairs quickly and without getting tired.' //
\endgl
\a
\begingl
\gla Kardeş-im-in iş-ler-i-ni {[} kendi-miz-i {yormadan }]AdvP\textsubscript{\textsc{adjunct}} ve {[} el-imiz-den gel-diğ-i {kadar }]PP\textsubscript{\textsc{adjunct}} hallet-ti-k. //
\glb brother-\textsc{1sg.poss}-\textsc{gen} business-\textsc{pl}-\textsc{3p}-\textsc{acc} self-\textsc{1pl.poss}-\textsc{acc} {without tiring} and hand-\textsc{1pl.poss}-\textsc{abl} come-\textsc{ptcp}-\textsc{3p} {inasmuch as}  {take care}-\textsc{pst}-\textsc{1pl} //
\glft `We took care of my brother's affairs as best we could and without tiring ourselves.' //
\endgl
\a
\begingl
\gla {[} Kardeş-im-in {iş-ler-i-ni }]NP\textsubscript{\textsc{obj}} ve {[} şehir {merkez-i-nde }]NP\textsubscript{\textsc{adjunct}} hallet-ti-k. //
\glb brother-\textsc{1sg.poss}-\textsc{gen} business-\textsc{pl}-\textsc{3p}-\textsc{acc} and city center-\textsc{3p}-\textsc{loc} {take care}-\textsc{pst}-\textsc{1pl} //
\glft `We took care of my brother's affairs and in downtown.' //
\endgl
\a
\begingl
\gla {[} Kardeş-im-in {iş-ler-i-ni }]NP\textsubscript{\textsc{obj}} ve + {[} {yorulmadan }]AdvP\textsubscript{\textsc{adjunct}} hallet-ti-k. //
\glb brother-\textsc{1sg.poss}-\textsc{gen} business-\textsc{pl}-\textsc{3p}-\textsc{acc} and {without getting tired} {take care}-\textsc{pst}-\textsc{1pl} //
\glft `We took care of my brother's affairs and without getting tired.' //
\endgl
\xe

\pex[exno=TS7, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS7} 
\a
\begingl
\gla Hayat-ın gerçek-ler-i-ni {[} kendi felsefe-si-ne {göre}]PP\textsubscript{\textsc{adjunct}} ve {[} ol-duğ-u {gibi}]PP\textsubscript{\textsc{adjunct}} kabul et-mişti. //
\glb life-\textsc{gen} reality-\textsc{pl}-\textsc{3p}-\textsc{acc} own philosophy-\textsc{3p}-\textsc{dat} {according to} and be-\textsc{ptcp}-\textsc{3p} like accept do-\textsc{pst.perf} //
\glft `(He/she) had accepted the facts of life according to his/her philosophy and as they were.' //
\endgl
\a
\begingl
\gla Hayat-ın gerçek-ler-i-ni {[} kendi felsefe-si-ne {göre}]PP\textsubscript{\textsc{adjunct}} ve {[} {yadırgamadan}]AdvP\textsubscript{\textsc{adjunct}} kabul et-mişti. //
\glb life-\textsc{gen} reality-\textsc{pl}-\textsc{3p}-\textsc{acc} own philosophy-\textsc{3p}-\textsc{dat} {according to} and {without hesitation} accept do-\textsc{pst.perf} //
\glft `He/she accepted the facts of life according to his/her own philosophy and without hesitation.' //
\endgl
\a
\begingl
\gla {[} Hayat-ın {gerçek-ler-i-ni}]NP\textsubscript{\textsc{obj}} ve {[} yaşa-dı-(ğ)ı en zor {an-lar-da}]NP\textsubscript{\textsc{adjunct}} kabul ed-ebil-mişti. //
\glb life-\textsc{gen} reality-\textsc{pl}-\textsc{3p}-\textsc{acc} and live-\textsc{pst}-\textsc{3p} most difficult moment-\textsc{pl}-\textsc{loc} accept do-\textsc{abil}-\textsc{pst.perf} //
\glft `(He/she) was able to accept the facts of life and in the most difficult moments of his/her life.' //
\endgl
\a
\begingl
\gla {[} Hayat-ın {gerçek-ler-i-ni}]NP\textsubscript{\textsc{obj}} ve {[} geçmiş-te-ki {gibi}]PP\textsubscript{\textsc{adjunct}} kabul edi-yor-du. //
\glb life-\textsc{gen} reality-\textsc{pl}-\textsc{3p}-\textsc{acc} and past-\textsc{loc}-\textsc{adjz} like accept do-\textsc{prog}-\textsc{pst} //
\glft `(He/she) accepted the facts of life and as they were in the past.' //
\endgl
\xe


\pex[exno=TS8, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS8}
\a
\begingl
\gla {[} {Saat-im-i}]NP\textsubscript{\textsc{obj}} ve {[} { telefon-um-u }]NP\textsubscript{\textsc{obj}} nazikçe çekmece-m-e koy-du-m. //
\glb {}watch-\textsc{1sg.poss}-\textsc{acc}{} and {phone}-\textsc{1sg.poss}-\textsc{acc}{} gently drawer-\textsc{1sg.poss}-\textsc{dat} put-\textsc{pst}-\textsc{1sg} //
\glft `I gently put my watch and my cellphone in my drawer.' //
\endgl
\a
\begingl\gla Saat-im-i {[} nazikçe{]}AdvP\textsubscript{\textsc{adjunct}} ve {[} dikkat-le{]}NP\textsubscript{\textsc{adjunct}}  çekmece-m-e koy-du-m. //
\glb watch-\textsc{1sg.poss}-\textsc{acc} gently and care-\textsc{ins} drawer-\textsc{1sg.poss}-\textsc{dat} put-\textsc{pst}-\textsc{1sg} //
\glft `I put my watch in my drawer gently and with care.' //
\endgl
\a
\begingl
\gla {[} Saat-im-i{]}NP\textsubscript{\textsc{obj}} ve {[} çekmece-m-e{]}NP\textsubscript{\textsc{obl}} nazikçe koy-du-m. //
\glb {}watch-\textsc{1sg.poss}-\textsc{acc}{} and {}drawer-\textsc{1sg.poss}-\textsc{dat}{} gently put-\textsc{pst}-\textsc{1sg} //
\glft `I gently put my watch and in my drawer.' //
\endgl
\a
\begingl
\gla {[} Saat-im-i{]}NP\textsubscript{\textsc{obj}} ve {[} nazikçe{]}AdvP\textsubscript{\textsc{adjunct}} + çekmece-m-e koy-du-m. //
\glb {}watch-\textsc{1sg.poss}-\textsc{acc}{} and {}gently{} drawer-\textsc{1sg.poss}-\textsc{dat}  put-\textsc{pst}-\textsc{1sg} //
\glft `I put my watch and gently in my drawer.' //
\endgl
\xe

\pex[exno=TS9, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS9}
\a
\begingl
\gla Günümüz salgın hastalık-lar-ı genelde ya {[} {hava]}NP\textsubscript{\textsc{adjunct}} {ya da} {[} kan {yol-u-yla]}NP\textsubscript{\textsc{adjunct}} bulaş-ır-lar. //
\glb {modern-day} contagious sickness-\textsc{pl}-\textsc{3p} generally either air or blood path-\textsc{3p}-\textsc{ins} spread-\textsc{aor}-\textsc{3pl} //
\glft `Today's epidemic diseases are generally transmitted either by air or blood.' //
\endgl
\a
\begingl
\gla Bu hastalık {[} kan yol-u {ile]}PP\textsubscript{\textsc{adjunct}} veya {[} mikrop bulaşmış {gıda-lar-dan]}NP\textsubscript{\textsc{adjunct}} yayıl-abil-ir. //
\glb this sickness blood path-\textsc{3p} with or microbe contaminated food-\textsc{pl}-\textsc{abl} spread-\textsc{abil}-\textsc{aor} //
\glft `This disease can be spread through blood or from contaminated food.' //
\endgl
\a
\begingl
\gla {[} Günümüz salgın {hastalık-lar-ı]}NP\textsubscript{\textsc{subj}} ve {[} kalabalık {hastane-ler-den]}NP\textsubscript{\textsc{adjunct}} bulaş-abil-ir. //
\glb {modern-day} contagious sickness-\textsc{pl}-\textsc{3p} and crowded hospital-\textsc{pl}-\textsc{abl} spread-\textsc{abil}-\textsc{aor}  //
\glft `Today's epidemic diseases and from crowded hospitals can be spread.' //
\endgl
\a
\begingl
\gla Günümüz {[} salgın {hastalık-lar-ı]}NP\textsubscript{\textsc{subj}} ve {[} {hızlı-ca]}AdvP\textsubscript{\textsc{adjunct}} bulaş-abil-ir. //
\glb {modern-day} contagious sickness-\textsc{pl}-\textsc{3p} and quick-ly spread-\textsc{abil}-\textsc{aor} //
\glft `Today's epidemic diseases and can be transmitted quickly.' //
\endgl
\xe

\pex[exno=TS10, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS10}
\a
\begingl
\gla Köy sakin-ler-i tedarik ed-il-en su-yu {[[} çamaşır yıka-mak ve bahçe {sula-mak}] {için}]PP\textsubscript{\textsc{adjunct}} kullan-ır-lar-dı. //
\glb village habitant-\textsc{pl}-\textsc{3p} supply do-\textsc{pass}-\textsc{adjz} water-\textsc{acc} {} laundry wash-\textsc{inf} and garden irrigate-\textsc{inf} for use-\textsc{aor}-\textsc{3pl}-\textsc{pst}   //
\glft `Village residents used the supplied water for washing clothes and watering gardens.' //
\endgl
\a
\begingl
\gla Köy sakin-ler-i tedarik ed-il-en su-yu çoğunlukla {[} çamaşır yıka-mak { için]}PP\textsubscript{\textsc{adjunct}} veya {[} {bahçe-ye]}NP\textsubscript{\textsc{adjunct}} kullan-ır-lar-dı. //
\glb village habitant-\textsc{pl}-\textsc{3p} supply do-\textsc{pass}-\textsc{adjz} water-\textsc{acc} mostly laundry wash-\textsc{inf} for or garden-\textsc{dat} use-\textsc{aor}-\textsc{3pl}-\textsc{pst} //
\glft `Village residents used the supplied water mostly for washing clothes or the garden.' //
\endgl
\a
\begingl
\gla Köy sakin-ler-i {[} tedarik ed-il-en {su-yu]}NP\textsubscript{\textsc{obj}} ve {[} {bahçe-ler-i-nde]}NP\textsubscript{\textsc{adjunct}}  kullan-ır-lar-dı. //
\glb village habitant-\textsc{pl}-\textsc{3p} supply do-\textsc{pass}-\textsc{adjz} water-\textsc{acc} and garden-\textsc{pl}-\textsc{3.poss}-\textsc{loc} use-\textsc{aor}-\textsc{3pl}-\textsc{pst}  //
\glft `Village residents used the supplied water and in their gardens.' //
\endgl
\a
\begingl
\gla Köy sakin-ler-i {[} tedarik ed-il-en {su-yu]}NP\textsubscript{\textsc{obj}} ve {[} tasarruf {ed-erek]}AdvP\textsubscript{\textsc{adjunct}} kullan-ır-lar-dı. //
\glb  village habitant-\textsc{pl}-\textsc{3p} supply do-\textsc{pass}-\textsc{adjz} water-\textsc{acc} and austerity do-\textsc{advz} use-\textsc{aor}-\textsc{3pl}-\textsc{pst} //
\glft `Village residents used the supplied water and sparingly.' //
\endgl
\xe

\pex[exno=TS11, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS11}
\a
\begingl
\gla Ya {[} {ders-ler-i-ni ]}NP\textsubscript{\textsc{obj}} {ya da} {[} ev {iş-ler-i-ni]}NP\textsubscript{\textsc{obj}} {yarım yamalak} yap-ar. //
\glb either homework-\textsc{pl}-\textsc{3p}-\textsc{acc} or house chore-\textsc{pl}-\textsc{3p}-\textsc{acc} {half-baked} do-\textsc{aor} //
\glft `(He/she) either does his/her homework or his/her chores half-baked.' //
\endgl
\a
\begingl
\gla Ders-ler-i-ni {[} {acele-yle ]}NP\textsubscript{\textsc{adjunct}} ve + {[} {{yarım yamalak}]}AdvP\textsubscript{\textsc{adjunct}} yap-tı. //
\glb homework-\textsc{pl}-\textsc{3p}-\textsc{acc} hurry-\textsc{ins} and {half-baked} do-\textsc{pst} //
\glft `(He/she) did his/her homework with haste and half-baked.' //
\endgl
\a
\begingl
\gla {[} {Oda-sı-nda]}NP\textsubscript{\textsc{adjunct}} ve {[} {ders-ler-i-ni]}NP\textsubscript{\textsc{obj}} acele-yle yap-tı. //
\glb room-\textsc{3p}-\textsc{loc} and homework-\textsc{pl}-\textsc{3p}-\textsc{acc} hurry-\textsc{ins} do-\textsc{pst} //
\glft `(He/she) did his/her homework and his/her room with haste.' //
\endgl
\a
\begingl
\gla {[} {Ders-ler-i-ni]}NP\textsubscript{\textsc{obj}} ve {[} {{yarım yamalak}]}AdvP\textsubscript{\textsc{adjunct}} yap-tı. //
\glb homework-\textsc{pl}-\textsc{3p}-\textsc{acc} and {half-baked} do-\textsc{pst} //
\glft `(He/she) did his/her homework and half-baked.' //
\endgl
\xe


\pex[exno=TS12, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS12}
\a
\begingl
\gla Kürsü-de {[} yerel minibüs {şoför-ler-i-ne ]}NP\textsubscript{\textsc{obl}} ve {[} {belediye-ye]}NP\textsubscript{\textsc{obl}} saydır-dı. //
\glb podium-\textsc{loc} local minibus driver-\textsc{pl}-\textsc{3p}-\textsc{dat} and municipality-\textsc{dat} curse-\textsc{pst} //
\glft `(He/she) cursed the local minibus drivers and the municipality on the podium.' //
\endgl
\a
\begingl
\gla Kürsü-de {[} yerel minibüs şoför-ler-i {hakkında ]}PP\textsubscript{\textsc{obl}} ve {[} {belediye-ye ]}NP\textsubscript{\textsc{obl}} saydır-dı. //
\glb podium-\textsc{loc} local minibus driver-\textsc{pl}-\textsc{3P} about and municipality-\textsc{dat} curse-\textsc{pst} //
\glft `On the podium, he/she cursed at local minibus drivers and municipality.' //
\endgl
\a
\begingl
\gla Kürsü-de {[} yerel minibüs {şoför-ler-i-ne ]}NP\textsubscript{\textsc{obl}} ve {[} kızgın bir {şekil-de ]}NP\textsubscript{\textsc{adjunct}}  saydır-dı. //
\glb podium-\textsc{loc} local minibus driver-\textsc{pl}-\textsc{3p}-\textsc{dat} and angry \textsc{indf.det} manner-\textsc{loc} curse-\textsc{pst} //
\glft `On the podium, (he/she) cursed the local minibus drivers and angrily.' //
\endgl
\a
\begingl
\gla Kürsü-de {[} yerel minibüs {şoför-ler-i-ne ]}NP\textsubscript{\textsc{obl}} ve {[} öfke {saç-arak ]}AdvP\textsubscript{\textsc{adjunct}}  saydır-dı. //
\glb podium-\textsc{loc} local minibus driver-\textsc{pl}-\textsc{3p}-\textsc{dat} and anger spill-\textsc{advz} curse-\textsc{pst} //
\glft `On the podium, (he/she) cursed the local minibus drivers and indignantly.' //
\endgl
\xe


\subsection{Coordination of unlike cases}


\pex[exno=TS1, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS1-case}
\a
\begingl
\gla Bugün {[} yeni araba {müze-si]}(DAT)\textsubscript{\textsc{obl}} ve {[} kent {orman-ı-na]}DAT\textsubscript{\textsc{obl}} git-ti-k. //
\glb today new car museum-\textsc{3p} and city forest-\textsc{3p}-\textsc{dat} go-\textsc{pst}-\textsc{1pl} //
\glft `Today we went to the new car museum and urban forest' //
\endgl
\a
\begingl
\gla Yeni araba müze-si-ne {[} metro {hat-tı-ndan]}ABL\textsubscript{\textsc{adjunct}} ve {[} M1 {tren-i-yle]}INS\textsubscript{\textsc{adjunct}} git-ti-k. //
\glb new car museum-\textsc{3p}-\textsc{dat} subway line-\textsc{3p}-\textsc{abl} and M1 train-\textsc{3p}-\textsc{ins} go-\textsc{pst}-\textsc{1pl} //
\glft `We went to the new car museum from the metro line and with the M1 train.' //
\endgl
\a
\begingl
\gla {[} Yeni araba {müze-si-ne]}DAT\textsubscript{\textsc{obl}} ve {[} {biz]}NOM\textsubscript{\textsc{subj}} metro-yla git-ti-k. //
\glb new car museum-\textsc{3p}-\textsc{dat} and we subway-\textsc{ins} go-\textsc{pst}-\textsc{1pl} //
\glft `We went and to the new car museum by the subway.' //
\endgl
\xe


\pex[exno=TS2, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS2-case}
\a
\begingl
\gla {[} {Devlet-ler]}NOM\textsubscript{\textsc{subj}} ve {[}iş {adam-lar-ı]}NOM\textsubscript{\textsc{subj}} dünya-da-ki herkes-e ekonomik işkence uygulu-yor-lar.//
\glb government-\textsc{pl} and business man-\textsc{pl}-\textsc{3p} world-\textsc{loc}-\textsc{adjz} everyone-\textsc{dat} economic torture inflict-\textsc{pres.prog}-\textsc{3pl}  //
\glft `Governments and businessmen inflict economic torture on everyone in the world.' //
\endgl
\a
\begingl
\gla Devlet-ler dünya-da-ki herkes-e hem {[} ekonomik {boyut-ta]}LOC\textsubscript{\textsc{adjunct}} {hem de} {[} sosyal {yol-lar-dan]}ABL\textsubscript{\textsc{adjunct}} işkence uygulu-yor-lar. //
\glb government-\textsc{pl} world-\textsc{loc}-\textsc{adjz} everyone-\textsc{dat} both economic dimension-\textsc{loc} and social method-\textsc{pl}-\textsc{abl} torture inflict-\textsc{pres.prog}-\textsc{3pl} //
\glft `Governments torture everyone in the world, both economically and socially.' //
\endgl
\a
\begingl
\gla {[} {Devlet-ler]}NOM\textsubscript{\textsc{subj}} ve {[} politik {neden-ler-le]}INS\textsubscript{\textsc{adjunct}} dünya-da-ki herkes-e ekonomik işkence uygulu-yor-lar. //
\glb government-\textsc{pl} and political reason-\textsc{pl}-\textsc{ins} world-\textsc{loc}-\textsc{adjz} everyone-\textsc{dat} economic torture inflict-\textsc{pres.prog}-\textsc{3pl} //
\glft `Governments and with political reasons torture everyone in the world.' //
\endgl
\xe


\pex[exno=TS3, glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS3-case}
\a
\begingl
\gla Okul-dan arkadaş-lar-ım {[} {ben-i]}ACC\textsubscript{\textsc{obj}} ve {[} {ablam-ı]}ACC\textsubscript{\textsc{obj}} büyük okul parti-si-ne çağır-dı-lar. //
\glb school-\textsc{abl} friend-\textsc{pl}-\textsc{1sg.poss} me-\textsc{acc} and sister-\textsc{acc} big school party-\textsc{3p}-\textsc{dat} invite-\textsc{pst}-\textsc{3pl} //
\glft `My friends from school invited me and my sister to the big school party.' //
\endgl
\a
\begingl
\gla Okul-dan arkadaş-lar-ım ben-i {[} heyecan {içerisi-nde]}LOC\textsubscript{\textsc{adjunct}} ve {[} {sabırsızlık-la]}INS\textsubscript{\textsc{adjunct}} büyük okul parti-si-ne çağır-dı-lar. //
\glb school-\textsc{abl} friend-\textsc{pl}-\textsc{1sg.poss} me-\textsc{acc} excitement inside-\textsc{loc} and impatience-\textsc{ins} big school party-\textsc{3p}-\textsc{dat} invite-\textsc{pst}-\textsc{3pl} //
\glft `My friends from school excitedly and impatiently invited me to the big school party.' //
\endgl
\a
\begingl
\gla Okul-dan arkadaş-lar-ım {[} {ben-i]}ACC\textsubscript{\textsc{obj}} ve {[} büyük okul {parti-si-ne]}DAT\textsubscript{\textsc{obl}} çağır-dı-lar. //
\glb school-\textsc{abl} friend-\textsc{pl}-\textsc{1sg.poss} me-\textsc{acc} and big school party-\textsc{3p}-\textsc{dat} invite-\textsc{pst}-\textsc{3pl} //
\glft `My friends from school invited me and to the big school party.' //
\endgl
\xe

\pex[exno=TS4,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS4-case}
\a
\begingl
\gla Oğlum-a internet-ten {[} şapka{]}NOM\textsubscript{\textsc{obj}} ve {[} ayakkabı{]}NOM\textsubscript{\textsc{obj}} al-dı-m //
\glb son-\textsc{dat} internet-\textsc{abl} hat and shoe buy-\textsc{pst}-\textsc{1sg} //
\glft `I bought my son a pair of shoes and a hat through the internet.' //
\endgl
\a
\begingl
\gla Oğlum-a {[} internet-ten{]}ABL\textsubscript{\textsc{adjunct}} ve {[} kredi + kart-ı-yla{]}INS\textsubscript{\textsc{adjunct}} ayakkabı al-dı-m //
\glb son-\textsc{dat} internet-\textsc{abl} and credit card-\textsc{3p}-\textsc{ins} shoe buy-\textsc{pst}-\textsc{1sg} //
\glft `I bought my son a pair of shoes through the internet and by credit card.' //
\endgl
\a
\begingl
\gla {[} Oğlum-a{]}DAT\textsubscript{\textsc{obl}} ve {[} iste-diğ-i ayakkabı-yı{]}ACC\textsubscript{\textsc{obj}} internet-ten al-dı-m //
\glb {}son-\textsc{dat}{} and {}want-\textsc{ptcp}-\textsc{3p} shoe-\textsc{acc}{} internet-\textsc{abl} buy-\textsc{pst}-\textsc{1sg} //
\glft `I bought my son and the pair of shoes he wanted through the internet.' //
\endgl
\xe

\pex[exno=TS5,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS5-case}
\a
\begingl
\gla {[} Kuzen-im{]}NOM\textsubscript{\textsc{subj}} ve {[} {ben]}NOM\textsubscript{\textsc{subj}} komşu-nun oğl-u-na eski kitap-lar-ımız-ı kapı-nın ağz-ı-ndan ver-di-k. //
\glb cousin-\textsc{1sg.poss} and I neighbor-\textsc{gen} son-\textsc{3p}-\textsc{dat} old book-\textsc{pl}-\textsc{1pl.poss}-\textsc{acc} door-\textsc{gen} mouth-\textsc{3p}-\textsc{abl} give-\textsc{pst}-\textsc{1pl} //
\glft `My cousin and I gave the neighbor's son our old books on the doorstep.' //
\endgl
\a
\begingl
\gla Eski kitap-lar-ımız-ı komşu-nun oğl-u-na {[} acele içi-nde{]}LOC\textsubscript{\textsc{adjunct}} ve {[} kapı-nın + ağz-ı-ndan{]}ABL\textsubscript{\textsc{adjunct}} ver-di-k. //
\glb old book-\textsc{pl}-\textsc{1pl.poss}-\textsc{acc} neighbor-\textsc{gen} son-\textsc{3p}-\textsc{dat} haste inside-\textsc{loc} and door-\textsc{gen} mouth-\textsc{3p}-\textsc{abl} give-\textsc{pst}-\textsc{1pl} //
\glft `(We) gave our old books to the neighbor's son in a hurry and on the doorstep.' //
\endgl
\a
\begingl
\gla Kuzen-im {[} komşu-nun oğl-u-na{]}DAT\textsubscript{\textsc{obl}} ve {[} eski kitap-lar-ı-nı{]}ACC\textsubscript{\textsc{obj}} kapı-nın ağz-ı-nda ver-di. //
\glb cousin-\textsc{1sg.poss} neighbor-\textsc{gen} son-\textsc{3p}-\textsc{dat} and old book-\textsc{pl}-\textsc{3p}-\textsc{acc} door-\textsc{gen} mouth-\textsc{3p}-\textsc{loc} give-\textsc{pst} //
\glft `My cousin gave the neighbor's son and his old books on the doorstep.' //
\endgl
\xe


\pex[exno=TS6,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS6-case}
\a
\begingl
\gla Günümüz genç-ler-i ya {[} sahil + kenarı-nda{]}LOC\textsubscript{\textsc{adjunct}} {ya da} {[} alışveriş + merkez-ler-i-nde{]}LOC\textsubscript{\textsc{adjunct}} yürü-r-ler. //
\glb modern-day youngster-\textsc{pl}-\textsc{3p} either coast side-\textsc{loc} or shopping center-\textsc{pl}-\textsc{loc} walk-\textsc{aor}-\textsc{3pl} //
\glft `Today's young people either walk by the beach or in shopping malls.' //
\endgl
\a
\begingl
\gla Günümüz genç-ler-i {[} el-ler-i-nde + telefon-la{]}INS\textsubscript{\textsc{adjunct}} ve {[} yol-un orta-sı-ndan{]}ABL\textsubscript{\textsc{adjunct}} yürüme-yi çok sev-er-ler. //
\glb modern-day youngster-\textsc{pl}-\textsc{3p} hand-\textsc{pl}-\textsc{3p}-\textsc{loc} telephone-\textsc{ins} and road-\textsc{gen} middle-\textsc{3p}-\textsc{abl} walking-\textsc{acc} much like-\textsc{aor}-\textsc{pl} //
\glft `Today's young people love to walk in the middle of the road and with their phones in their hands.' //
\endgl
\a
\begingl
\gla Günümüz genç-ler-i ya {[} sahil + kenarı-nda{]}LOC\textsubscript{\textsc{adjunct}} {ya da} {[} alışveriş + merkez-ler-i-ne{]}DAT\textsubscript{\textsc{obl}} yürü-r-ler. //
\glb modern-day youngster-\textsc{pl}-\textsc{3p} either coast side-\textsc{loc} or shopping center-\textsc{pl}-\textsc{dat} walk-\textsc{aor}-\textsc{3pl} //
\glft `Today's young people either walk by the beach or to the malls.' //
\endgl
\xe

\pex[exno=TS7,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS7-case}
\a
\begingl
\gla Yazar yeni kitab-ı-nı {[} bunalım-da-ki + ergen-ler-e{]}DAT\textsubscript{\textsc{obl}} ve {[} genç yetişkin-ler-e{]}DAT\textsubscript{\textsc{obl}} ada-dı. //
\glb author new book-\textsc{3p}-\textsc{acc} depression-\textsc{loc}-\textsc{adjz} adolescent-\textsc{pl}-\textsc{dat} and young adult-\textsc{pl}-\textsc{dat} dedicate-\textsc{pst} //
\glft `The author dedicated (his/her) new book to depressed adolescents and young adults.' //
\endgl
\a
\begingl
\gla Yazar yeni kitab-ı-nı bunalım-da-ki genç yetişkin-ler-e {[} mütevazilik-le{]}INS\textsubscript{\textsc{adjunct}} ve {[} kalp-ten{]}ABL\textsubscript{\textsc{adjunct}} ada-dı. //
\glb author new book-\textsc{3p}-\textsc{acc} depression-\textsc{loc}-\textsc{adjz} young adult-\textsc{pl}-\textsc{dat} modesty-\textsc{ins} and heart-\textsc{abl} dedicate-\textsc{pst} //
\glft `The author humbly and wholeheartedly dedicated (his/her) new book to depressed young adults.' //
\endgl
\a
\begingl
\gla Yazar yeni kitab-ı-nı {[} bunalım-da-ki +  ergen-ler-e{]}DAT\textsubscript{\textsc{obl}} ve {[} kalp-ten{]}ABL\textsubscript{\textsc{adjunct}} ada-dı. //
\glb author new book-\textsc{3p}-\textsc{acc} depression-\textsc{loc}-\textsc{adjz}  adolescent-\textsc{pl}-\textsc{dat} and heart-\textsc{abl} dedicate-\textsc{pst} //
\glft `The author dedicated (his/her) new book to depressed adolescents and from the heart.' //
\endgl
\xe

\pex[exno=TS8,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS8-case}
\a
\begingl
\gla {[} İhtiyar heyet-i{]}NOM\textsubscript{\textsc{subj}} ve {[} seçkin kimse-ler{]}NOM\textsubscript{\textsc{subj}} el kadar çocuğ-u kral ilan et-ti-ler. //
\glb elder council-\textsc{3p} and distinguished people-\textsc{pl} hand {inasmuch as} child-\textsc{acc} king proclamation do-\textsc{pst}-\textsc{3pl} //
\glft `The council of elders and distinguished people proclaimed the very young child as king.' //
\endgl
\a
\begingl
\gla İhtiyar heyet-i el kadar çocuğ-u {[} yüksek koltuk-lar-ı-ndan{]}ABL\textsubscript{\textsc{adjunct}} ve {[} gurur-lu bir eda-yla{]}INS\textsubscript{\textsc{adjunct}} kral ilan et-ti-ler. //
\glb elder council-\textsc{3p} hand {inasmuch as} child-\textsc{acc} high seat-\textsc{pl}-\textsc{3p}-\textsc{abl} and proud-\textsc{adjz} \textsc{indf.det} manner-\textsc{ins} king proclamation do-\textsc{pst}-\textsc{3pl} //
\glft 'The council of elders proclaimed the very young child as king from their high seats and proudly.' //
\endgl
\a
\begingl
\gla İhtiyar heyet-i {[} el kadar çocuğ-u{]}ACC\textsubscript{\textsc{obj}} ve {[} oturum-da{]}LOC\textsubscript{\textsc{adjunct}} kral ilan et-ti-ler. //
\glb elder council-\textsc{3p} hand {inasmuch as} child-\textsc{acc} and session-\textsc{loc} king proclamation do-\textsc{pst}-\textsc{3pl}  //
\glft 'The council of elders proclaimed the very young child and in the session.' //
\endgl
\xe


\pex[exno=TS9,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS9-case}
\a
\begingl
\gla Beşiktaş defans-ı kale-si-ni {[} soğukkanlılık{]}(INS)\textsubscript{\textsc{adjunct}} ve {[} disiplin-le{]}INS\textsubscript{\textsc{adjunct}} hayati bir gol-den koru-du. //
\glb Beşiktaş defense-\textsc{3p} goal-\textsc{3p}-\textsc{acc} calmness and discipline-\textsc{ins} vital \textsc{indf.det} goal-\textsc{abl} protect-\textsc{pst} //
\glft Beşiktaş defense protected its goal from an important score with composure and discipline.' //
\endgl
\a
\begingl
\gla Beşiktaş defans-ı kale-si-ni {[} soğukkanlılık-la{]}INS\textsubscript{\textsc{adjunct}} ve {[} dayanışma içi-nde{]}LOC\textsubscript{\textsc{adjunct}} koruma-yı başar-dı. //
\glb Beşiktaş defense-\textsc{3p} goal-\textsc{3p}-\textsc{acc} calmness-\textsc{ins} and solidarity inside-\textsc{loc} protection-\textsc{acc} succeed-\textsc{pst} //
\glft Beşiktaş defense succeeded in protecting its goal with composure and in solidarity.' //
\endgl
\a
\begingl
\gla Beşiktaş defans-ı {[} kale-yi{]}ACC\textsubscript{\textsc{obj}} ve {[} ceza saha-sı-nda{]}LOC\textsubscript{\textsc{adjunct}} hayati bir gol-den koru-yabil-di. //
\glb Beşiktaş defense-\textsc{3p} goal-\textsc{acc} and penalty area-\textsc{3p}-\textsc{loc} vital \textsc{indf.det} goal-\textsc{abl} protect-\textsc{abil}-\textsc{pst} //
\glft `Beşiktaş defense was able to protect the goal and in the penalty area from a vital score.' //
\endgl
\xe

\pex[exno=TS10,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS10-case}
\a
\begingl
\gla {[} Küçük çocuk{]}NOM\textsubscript{\textsc{subj}} ve {[} arkadaş-ı{]}NOM\textsubscript{\textsc{subj}} akşam yemeği-ni kendi masa-lar-ı-nda ye-di-ler. //
\glb little child and friend-\textsc{3p} evening meal-\textsc{acc} own table-\textsc{pl}-\textsc{3p}-\textsc{loc} eat-\textsc{pst}-\textsc{pl} //
\glft `The little child and their friend had dinner at their own table.' //
\endgl
\a
\begingl
\gla Küçük çocuk akşam yemeği-ni {[} kendi + masa-sı-nda{]}LOC\textsubscript{\textsc{adjunct}} ve {[} anne-si-nin + el-i-nden{]}ABL\textsubscript{\textsc{adjunct}} ye-di. //
\glb little child evening meal-\textsc{acc} own table-\textsc{3p}-\textsc{loc} and mother-\textsc{3p}-\textsc{gen} hand-\textsc{3p}-\textsc{abl} eat-\textsc{pst} //
\glft `The little child had dinner at his/her own table and from his/her mother's hand.' //
\endgl
\a
\begingl
\gla Küçük çocuk {[} akşam yemeği-ni{]}ACC\textsubscript{\textsc{obj}} ve {[} anne-si-nin el-i-nden{]}ABL\textsubscript{\textsc{adjunct}} ye-di. //
\glb little child evening meal-\textsc{acc} and mother-\textsc{3p}-\textsc{gen} hand-\textsc{3p}-\textsc{abl} eat-\textsc{pst} //
\glft `The little child had dinner and from his/her mother's hand.' //
\endgl
\xe

\pex[exno=TS11,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS11-case}
\a
\begingl
\gla Dünya-da-ki {[} yenilik-ler-i{]}ACC\textsubscript{\textsc{obj}} ve {[} gelişme-ler-i{]}ACC\textsubscript{\textsc{obj}} internet-ten takip ed-iyor-um. //
\glb world-\textsc{loc}-\textsc{adjz} innovation-\textsc{pl}-\textsc{acc} and devolopment-\textsc{pl}-\textsc{acc} internet-\textsc{abl} follow do-\textsc{pres.prog}-\textsc{1sg}//
\glft'I follow the innovations and developments in the world over the internet.'//
\endgl
\a
\begingl
\gla Dünya-da-ki gelişme-ler-i {[} küçük yurt oda-m-da{]}LOC\textsubscript{\textsc{adjunct}} ve {[} internet-ten{]}ABL\textsubscript{\textsc{adjunct}} takip + ed-iyor-um. //
\glb world-\textsc{loc}-\textsc{adjz} development-\textsc{pl}-\textsc{acc} small dormitory room-\textsc{1sg.poss}-\textsc{loc} and internet-\textsc{abl} follow do-\textsc{pres.prog}-\textsc{1sg}//
\glft'I follow the developments in the world in my small dormitory room and over the internet.'//
\endgl
\a
\begingl
\gla Dünya-da-ki {[} gelişme-ler-i{]}ACC\textsubscript{\textsc{obj}} ve + {[} internet-ten{]}ABL\textsubscript{\textsc{adjunct}} takip ed-iyor-um. //
\glb World-\textsc{loc}-\textsc{adjz} development-\textsc{pl}-\textsc{acc} and internet-\textsc{abl} follow do-\textsc{pres.prog}-\textsc{1sg}//
\glft'I follow the developments in the world and over the internet.'//
\endgl
\xe

\pex[exno=TS12,glspace=!1em,everygla={},everyglb={},aboveglbskip=-.15ex, interpartskip=15pt]
\label{TS12-case}
\a
\begingl
\gla {[} Park görevli-si-ne{]}DAT\textsubscript{\textsc{obl}} ve {[} park-ın sahib-i-ne{]}DAT\textsubscript{\textsc{obl}} ödeme-yi mobil uygulama-dan + yap-tığ-ım-ı söyle-di-m. //
\glb park attendant-\textsc{3p}-\textsc{dat} and park-\textsc{gen} owner-\textsc{3p}-\textsc{dat} payment-\textsc{acc} mobile application-\textsc{abl} make-\textsc{ptcp}-\textsc{1sg.poss}-\textsc{acc} say-\textsc{pst}-\textsc{1sg} //
\glft `I told the park attendant and the owner of the park that I made the payment through the mobile app.' //
\endgl
\a
\begingl
\gla Park görevli-si-ne ödeme-m-i {[} mobil uygulama-dan{]}ABL\textsubscript{\textsc{adjunct}} ve {[} hediye kart-ı-yla{]}INS\textsubscript{\textsc{adjunct}} + yap-tığ-ım-ı söyle-di-m. //
\glb park attendant-\textsc{3p}-\textsc{dat} payment-\textsc{1sg.poss}-\textsc{acc} mobile application-\textsc{abl} and gift card-\textsc{3p}-\textsc{ins} make-\textsc{ptcp}-\textsc{1sg.poss}-\textsc{acc} say-\textsc{pst}-\textsc{1sg} //
\glft `I told the parking attendant that I made my payment from the mobile app and with gift card.' //
\endgl
\a
\begingl
\gla Park görevli-si-ne {[} ödeme-m-i{]}ACC\textsubscript{\textsc{obj}} ve {[} mobil uygulama-dan{]}ABL\textsubscript{\textsc{adjunct}} yap-tığ-ım-ı söyle-di-m. //
\glb park attendant-\textsc{3p}-\textsc{dat} payment-\textsc{1sg.poss}-\textsc{acc} and mobile application-\textsc{abl} make-\textsc{ptcp}-\textsc{1sg.poss}-\textsc{acc} say-\textsc{pst}-\textsc{1sg} //
\glft `I told the parking attendant that I made my payment and from the mobile app.' //
\endgl
\xe
